Active Learning with Sentence Error Classification in Machine Translation

### 2020-11-13 Paper/data-processing.tex
small update

We divided data processing into \emph{x} steps -
    (1) Mapping different error labels to five main error labels;
    (2) Combining the dataset with both correct and incorrect sentences; 
    (3) Encoding error labels and building an error vector;
    (4) Ensuring sentence "uniqueness"; and

>>>>

We divided data processing into \emph{x} steps -
    (1) Mapping different error labels to five main error labels;
    (2) Combining the dataset with both correct and incorrect sentences; 
    (3) Encoding error labels and building an error vector; and
    (4) Ensuring sentence "uniqueness";
